---
title: "googleVis"
author: "Damjan Stefanovski"
date: "August 30, 2017"
output: html_document
---
## Example of Plots and Charts with Vis

```{r gv, results="asis", cache=TRUE}
suppressPackageStartupMessages(library(googleVis))
M <- gvisMotionChart(Fruits, "Fruit", "Year",
                     options=list(width=600, height=400))
print(M, "chart")



```
#Charts in googleVis

"gvis + ChartType"
Motion charts: gvisMotionChart
Interactive maps: gvisGeoChart
Interactive tables: gvisTable
Line charts: gvisLineChart
Bar charts: gvisColumnChart
Tree maps: gvisTreeMap

http://cran.r-project.org/web/packages/googleVis/googleVis.pdf

# Plots on maps 

```{r}
G <- gvisGeoChart(Exports, locationvar="Country",
                  colorvar="Profit",options=list(width=800, height=600))
print(G,"chart")

```

Specifying Region 

```{r}
G2 <- gvisGeoChart(Exports, locationvar="Country",
                  colorvar="Profit",options=list(width=600, height=400,region="150"))
print(G2,"chart")
```

More options line chart

```{r}
df <- data.frame(label=c("US", "GB", "BR"), val1=c(1,3,4), val2=c(23,12,32))
Line <- gvisLineChart(df, xvar="label", yvar=c("val1","val2"),
        options=list(title="Hello World", legend="bottom",
                titleTextStyle="{color:'red', fontSize:18}",                         
                vAxis="{gridlines:{color:'red', count:3}}",
                hAxis="{title:'My Label', titleTextStyle:{color:'blue'}}",
                series="[{color:'green', targetAxisIndex: 0}, 
                         {color: 'blue',targetAxisIndex:1}]",
                vAxes="[{title:'Value 1 (%)', format:'##,######%'}, 
                                  {title:'Value 2 (\U00A3)'}]",                          
                curveType="function", width=500, height=300                         
                ))
print(Line, "chart")
```

#Combining multiple plots together

```{r}
G <- gvisGeoChart(Exports, "Country", "Profit",options=list(width=200, height=100))
T1 <- gvisTable(Exports,options=list(width=200, height=270))
M <- gvisMotionChart(Fruits, "Fruit", "Year", options=list(width=800, height=670))
GT <- gvisMerge(G,T1, horizontal=FALSE)
GTM <- gvisMerge(GT, M, horizontal=TRUE,tableOptions="bgcolor=\"#CCCCCC\" cellspacing=10")
```
Things you can do with Google Vis

The visualizations can be embedded in websites with HTML code
Dynamic visualizations can be built with Shiny, Rook, and R.rsp
Embed them in R markdown based documents
Set results="asis" in the chunk options
Can be used with knitr and slidify





